---
title: "Stattistical_ML_Assignment 1"
output: html_document
---

# Exercise 1

__A moviestreamingcompanycollecteddataonmovieviewingsofapoolof4187subscribers,withtheintentofdeploying a more eﬀicient movie recommendation system. For each subscriber, the data record the movies seen in a given period. The following tables report summaries of the frequencies of occurrence of 4 movies in particular: The Lighthouse, Parasite, The Wind, Shimmer Lake.__



# Exercise 2 
Dataset data_spotify_songs.rda contains data about audio features for a collection of songs extracted from the music streaming platform Spotify. The songs are classified into three genres: acoustic, pop, rock. For each song, measurementsaboutaudiofeaturesandpopularityarerecorded;moreinformationabouttheaudiofeaturesisavailable here:

https://developer.spotify.com/documentation/web-api/reference/tracks/get-audio-features/

Perform a cluster analysis of the audio features data using k-means: 

1. Consider a range of values of𝐾from 1 to 10. Select the appropriate number of clusters for this data.

2. Compare the clustering obtained to the classification into genres, providing a brief interpretation of the clusters.


__Setting working Directory__
```{r working directory}
setwd('G:\\My Drive\\spring_semester\\statistical_ml\\assignments\\assignment1')
```


__Loading Data__
```{r load data}
load('data_spotify_songs.rda')
```

__Inspecting data__
```{r Inspect}

str(spotify) # to check the number of variable their types and number of observations in the data.
head(spotify) # to get an overview of data

song = spotify[, -c(1:3)] # removing the column containg genre of the songs and other factor variables like song name and artist.

scale(song)
pairs(song, gap = 0, pch = 19, col = adjustcolor(1, 0.4))
```

```{r}
fitkm = kmeans(song, centers = 3)


```

